\documentclass{article}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{tabu}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{wrapfig}
\usepackage{multirow}
\setlength{\columnsep}{0.3in}

\geometry{letterpaper, portrait, margin=1in}

\begin{document}


\begin{multicols}{2}
\begin{flushleft}
	
	\textsf{\Huge Emily Weil} 
\end{flushleft}

\columnbreak
\begin{flushright}
	\begin{tabular}{r | l}
	emweilx@gmail.com & 1000 Boxwood Court \\
	201-739-5248 & Mahwah, NJ 07430 \\
	\end{tabular}
\end{flushright}
\end{multicols}

\hfill \break

{\parindent0pt
\textsf{\Large Education}\\

Harvard University \hfill Cambridge, MA \\ 
\textit{A.B. Degree in Computer Science} \hfill May 2018 

Secondary field in Visual and Environmental Studies, Studio track.

Relevant Coursework: Systems Security, Distributed Systems, Data Structures and Algorithms, Operating Systems, Artificial Intelligence, Machine Learning, History of Democracy & Technology, History of Artificial Intelligence. \\ 

\textsf{\large Experience}\\

The Berkman Klein Center for Internet and Society \hfill Cambridge, MA\\
\textit{Berklett Cybersecurity Intern} \hfill June 2018-August 2018\\
Researched and wrote a report on Internet of Things surveillance. \\
  
Harvard University \hfill Cambridge, MA\\
Teaching Fellow for CS61: Systems Programming and Machine Organization \hfill Fall 2017\\
Teaching Fellow for CS1: Great Ideas in Computer Science \hfill Spring 2017, Summer 2017	
\begin{itemize} \itemsep -2pt
	\item Teach weekly supplementary lectures for college and graduate students.
	\item Hold unstructured extra help sessions.
\end{itemize}

Cooper Hewitt, Smithsonian Design Museum \hfill New York, NY\\
\textit{Cross-Platform Publishing Intern} \hfill June 2016-August 2016
\begin{itemize}	\itemsep -2pt
	\item Created workflow to convert books designed for print into EPUB files for online distribution with a combination of Adobe InDesign features and Python scripts.
	\item Designed various print materials for the museum, including postcards and exhibition posters.
	\item Proofed and assisted in design decisions for museum publications. 
\end{itemize}

Let’s Go Publications \hfill Cambridge, MA\\
\textit{Product Manager} \hfill June 2015-August 2015	
\begin{itemize} \itemsep -2pt
	\item Typeset and redesigned books, including Inside Harvard: Third Edition and Comp Harvard.
	\item Maintained and extended functionality of website, letsgo.com, with over 6,000 weekly visits. 
\end{itemize}

The Jewish Museum \hfill New York, NY
Teen Intern \hfill May 2013-May 2014 
\begin{itemize} \itemsep -2pt
	\item Worked with educators to design and run children’s art programs for current exhibitions.
\end{itemize}

\textsf{\large Leadership and Activities}\\
The Harvard Advocate									Cambridge, MA
Design Editor						   	     December 2015 – December 2016
-	Led board of 13 designers.
-	Managed and finalize layout and aesthetic of oldest continuously published college art and literary magazine in United States.
-	Collaborated with Tech department to create and design digital anthology of published works. 

Harvard Radio Broadcasting								Cambridge, MA
Chief Engineer								January 2015 – January 2016
-	Diagnosed and repaired functionality issues in broadcasting and studio equipment.
-	Responded to accessibility questions from listenership in greater Boston area and online.

\textsf{\large Skills and Interests}\\
Technical: C, Java, Python, OCaml, PHP, C++, HTML/CSS, LaTeX, Wordpress, Adobe Photoshop, Adobe Illustrator, Adobe InDesign.
Language: Spanish (proficient), French (beginner).
Interests: Graphic Design, Printmaking, Photography, Visiting museums, Deejaying. 

}

\end{document}
